BTM

### 2021-05-12 btm_gh.Rmd
Update doc, add BTM Vignette
Make all vignettes not emitting constant changing information

@@

```{r}
trump_btm <- BTM(trump_dat, k = 8, iter = 500, trace = 10)
```

>>>>

---
title: "BTM"
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
set.seed(42)
```

@@

```{r, message = FALSE, results = 'hide', warning = FALSE}
trump_btm <- BTM(trump_dat, k = 8, iter = 500, trace = 10)
```
